Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-31 Paper/chokepoint.tex
Explained in-to-out and out-to-in

We define a BGP path of length $n$ from source AS $a_0$ to destination AS $a_n$
as a sequence $p_{1\rightsquigarrow n} = \{a_i : i \in [1,n]\}$.  We define a
\textit{routing tree} to be a tree rooted at a single destination AS and
composed of every acceptable BGP path from the various source ASes that can
reach the destination AS.\Ben[inline]{Is this always a tree? Seems like it
could be a DAG sometimes (especially if random choices are made). Also do we
need to define routing trees if we only really work on the path}  The
chokepoint potential of a border AS is the ratio of the number of paths in (or out of) the country that contain the border AS to
the total number of paths in (or out of) the same country.
%intercepted by all border ASes belonging to
%the same nation.
Formally, for country $c$, let $P = \{p_{i \rightsquigarrow
j} : g(a_i)=c \text{ and } g(a_j)\neq c\} $, i.e.\ the set of all paths
originating in $c$ and ending outside $c$. Then the chokepoint potential,
$cp(\cdot)$, of a border AS $a_u$ with $g(a_u) = c$ is
\Steph[inline]{How do we count a parth that originates in a country, routes through a different country, and terminates in the original country?  That case is relevant in US law.}
\begin{equation}
  \label{eq:chokepoint}
  cp(a_u) = \frac{|\{p: p \in P \text{ and } a_u \in P\}|}{|P|}
\end{equation}

@@

%For instance, take
%a border AS $b$, belonging to country $c$.  If $P_c$ is the set of paths in to
%or out of country $c$ and $B_p$ is the set of border ASes within path $p$, then
%the chokepoint potential of $b$, $CP(b)$ is defined formally in equation
%\ref{eqn:chokePointPotential}. 
%This is calculated seperately for in-to-out paths (those starting from a source
%in the country in question) and out-to-in paths.
The incoming chokepoint
potential for a nations is illustrated in \figurename
\ref{fig:chokepoint}.

\Ben[inline]{A couple of questions here. Why mess with incoming (out to in) and
outgoing (in to out) measures? Can we just define it as $\frac{|p_{in}| +
|p_{out}|}{|P_{in}| + |P_{out}|}$, that is the incoming and outgoing paths over
the total paths? Would this be that much different? Is there are an argument to
be made that out-to-in or in-to-out is a better? My guess is they are all
pretty correlated, I can check on that}.
% Formal Definition
%\begin{equation}\label{eqn:chokePointPotential}
%CP(b) = \frac{|\{p \in P_c \textrm{ s.t. } \{b\} \subseteq B_p\}|}{\sum_{p \in P_c}|B_p|}
%\end{equation}

>>>>

We define a BGP path of length $n$ from source AS $a_0$ to destination AS $a_n$
as a sequence $p_{1\rightsquigarrow n} = \{a_i : i \in [1,n]\}$.  We define a
\textit{routing tree} to be a tree rooted at a single destination AS and
composed of every acceptable BGP path from the various source ASes that can
reach the destination AS. Note that if multiple paths exist from a source
to a destination, the routing tree is technicailly a DAG, but we use the traditional convention and call
all such data structures routing trees. The
chokepoint potential of a border AS is the ratio of the number of paths in (or out of) the country that contain the border AS to
the total number of paths in (or out of) the same country.
%intercepted by all border ASes belonging to
%the same nation.
Formally, for country $c$, let $P = \{p_{i \rightsquigarrow
j} : g(a_i)=c \text{ and } g(a_j)\neq c\} $, i.e.\ the set of all paths
originating in $c$ and ending outside $c$. Then the chokepoint potential,
$cp(\cdot)$, of a border AS $a_u$ with $g(a_u) = c$ is
\Steph[inline]{How do we count a parth that originates in a country, routes through a different country, and terminates in the original country?  That case is relevant in US law.}
\begin{equation}
  \label{eq:chokepoint}
  cp(a_u) = \frac{|\{p: p \in P \text{ and } a_u \in P\}|}{|P|}
\end{equation}

@@

%For instance, take
%a border AS $b$, belonging to country $c$.  If $P_c$ is the set of paths in to
%or out of country $c$ and $B_p$ is the set of border ASes within path $p$, then
%the chokepoint potential of $b$, $CP(b)$ is defined formally in equation
%\ref{eqn:chokePointPotential}. 
%This is calculated seperately for in-to-out paths (those starting from a source
%in the country in question) and out-to-in paths.
The incoming chokepoint
potential for a nations is illustrated in \figurename
\ref{fig:chokepoint}. We define both $cpo$ and $cpi$ because past work
has revealed that country-level paths are often asymmetric, meaning that the
forward path from AS $a$ to AS $b$ does not necessarily match the reverse path
\cite{characterizingAndAvoiding}.
